Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-05 manuscript/manuscript.tex
change 'avg' to 'H1+H3 average'

\begin{table}[t!]
\caption{\label{tab:empirical_data}
Model comparison for Fig.~\ref{fig:empirical_trees}.}
     \begin{tabular}{ccccc}
        \hline
          Model & $\Delta$AIC & Log Likelihood & Parameters\\ \hline
       	ExpCM + $\Gamma\omega$ (average) & 0.00 & -48751.16 & $\omega$ = (0.19,  0.50,  0.90,  1.86), $\beta=1.70$, $\kappa=3.73$\\
	ExpCM (average) & 949.70 & -49227.01 & $\beta=1.78$, $\kappa=3.40$, $\omega=0.15$\\
	ExpCM + $\Gamma\omega$ (H1) & 1306.44 & -49404.38  & $\omega$ = (0.13 ,  0.44,  0.91,  2.16), $\beta=1.12$, $\kappa=3.64$\\
	ExpCM + $\Gamma\omega$ (H3) & 1737.40 & -49619.86 & $\omega$ = (0.09,  0.33,  0.72,  1.77), $\beta=1.28$, $\kappa=3.71$\\
	ExpCM (H1) & 2555.58 & -50029.95 & $\beta=1.22$, $\kappa=3.24$, $\omega=0.13$\\
	ExpCM (H3) & 3196.50 & -50350.41 & $\beta=1.45$, $\kappa=3.38$, $\omega=0.12$\\
	GY94 + $\Gamma\omega$ & 4719.34 & -51105.83 & $\omega$ = (0.00,  0.03,  0.08,  0.26), $\kappa=3.18$\\
	GY94 & 7624.64 & -52559.48  & $\kappa=2.89$, $\omega=0.07$\\
      \end{tabular}
\end{table}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.5\textwidth]{figures/phylobayes.pdf}}
\caption{\label{fig:phylobayes}
\textbf{Comparison of ExpCM and phylobayes}
}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{fig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\skhcomment{I need to change the $\beta$ value when the new \texttt{phydms} results finish running.}
\end{figure}

>>>>

\begin{table}[t!]
\caption{\label{tab:empirical_data}
Model comparison for Fig.~\ref{fig:empirical_trees}.}
     \begin{tabular}{ccccc}
        \hline
          Model & $\Delta$AIC & Log Likelihood & Parameters\\ \hline
       	ExpCM + $\Gamma\omega$ (H1+H3 average) & 0.00 & -48751.16 & $\omega$ = (0.19,  0.50,  0.90,  1.86), $\beta=1.70$, $\kappa=3.73$\\
	ExpCM (H1+H3 average) & 949.70 & -49227.01 & $\beta=1.78$, $\kappa=3.40$, $\omega=0.15$\\
	ExpCM + $\Gamma\omega$ (H1) & 1306.44 & -49404.38  & $\omega$ = (0.13 ,  0.44,  0.91,  2.16), $\beta=1.12$, $\kappa=3.64$\\
	ExpCM + $\Gamma\omega$ (H3) & 1737.40 & -49619.86 & $\omega$ = (0.09,  0.33,  0.72,  1.77), $\beta=1.28$, $\kappa=3.71$\\
	ExpCM (H1) & 2555.58 & -50029.95 & $\beta=1.22$, $\kappa=3.24$, $\omega=0.13$\\
	ExpCM (H3) & 3196.50 & -50350.41 & $\beta=1.45$, $\kappa=3.38$, $\omega=0.12$\\
	GY94 + $\Gamma\omega$ & 4719.34 & -51105.83 & $\omega$ = (0.00,  0.03,  0.08,  0.26), $\kappa=3.18$\\
	GY94 & 7624.64 & -52559.48  & $\kappa=2.89$, $\omega=0.07$\\
      \end{tabular}
\end{table}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.5\textwidth]{figures/phylobayes.pdf}}
\caption{\label{fig:phylobayes}
\textbf{Comparison of ExpCM and phylobayes}
\skhcomment{y=x line too faint?}
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{fig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\skhcomment{I need to change the $\beta$ value when the new \texttt{phydms} results finish running.}
\end{suppfig}
